---
title: "COMPSCIX 415.2 Homework 7"
author: "Kate Mellon"
date: "3/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####  Exercise 1

In the train.csv data set there are 1,460 observations and 81 columns.

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
train <- read.csv("/users/katie/downloads/train.csv")
  glimpse(train)

```

#### Exercise 2

```{r}

library(tidyverse)
library(broom)

# When taking a random sample, it is often useful to set a seed so that
# your work is reproducible. Setting a seed will guarantee that the same
# random sample will be generated every time, so long as you always set the
# same seed beforehand

train <- read.csv("/users/katie/downloads/train.csv")

set.seed(29283)

# This data already has an Id column which we can make use of.
# Let's create our training set using sample_frac. Fill in the blank.

train_set <- train %>% sample_frac(0.7)

# let's create our testing set using the Id column. Fill in the blanks.

test_set <- train %>% filter(!(train$Id %in% train_set$Id))
```

#### Exercise 3

```{r}
# Fit a model with intercept only
mod_0 <- lm(SalePrice ~ 1, data = train_set)
# Double-check that the average SalePrice is equal to our model's coefficient
mean(train_set$SalePrice)
tidy(mod_0)
# Check the R-squared
glance(mod_0)

```

#### Exercise 4

How would you interpret the coefficients on GrLivArea and OverallQual?

How would you interpret the coefficient on NeighborhoodBrkSide?

Are the features significant?

Are the features practically significant?

Is the model a good fit (to the training set)?

```{r}
mod_1 <- lm(SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = train_set)

tidy(mod_1)
  
```

#### Exercise 5

```{r}
test_predictions <- predict(mod_1, newdata = test_set)

(rmse <- sqrt(mean((test_set$SalePrice - test_predictions)^2)))

```

#### Exercise 6

#### Exercise 7

```{r}
sim1a <- tibble(
x = rep(1:10, each = 3),
y = x * 1.5 + 6 + rt(length(x), df = 2)
)

sim1a_rm <- lm(y~x, data = sim1a)

sim1a_rm %>% ggplot(mapping=aes(x,y)) +
  geom_point()

```



