---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Kate Mellon"
date: "3/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

My Github repository for the midterm can be found at this URL: https://github.com/kmellon/compscix-415-2-assignments.git

## R Markdown

####The tidyverse packages

1.) The tidyverse packages associated with the tasks below are as follows:

Plotting - ggplot

Data munging/wrangling - dplyr

Reshaping (speading and gathering) data - tydr

Importing/exporting data - readr


2.) Two functions used from each package I listed above for the tasks below are as follows:

Plotting - ggplot(), geom_point()

Data munging/wrangling - filter(), select()

Reshaping data - spread(), gather()

Importing/exporting data - read_csv, write_csv

####R Basics

1.) 
```{r}
My_data.name___is.too00ooLong <- c( 1 , 2 , 3 )

```

2.) 

```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')

```

3.) The values in the vector ...
```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```


####Data Import/Export

1.)

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
rail_data <- read.table("/users/katie/downloads/rail_trail.txt")
  glimpse(rail_data)
```

2.)
```{r}
saveRDS(rail_data,"rail_trail.rds")
new_file <- readRDS("rail_trail.rds")
glimpse(new_file)
```


####Visualization

1.) 
- The coloring in the graphic is confusing because a separate color is used to distinguish gender, while age is represented as all one color.
- 
-

2.)

```{r}

ggplot(data=diamonds) +
  geom_boxplot(mapping=aes(x=carat, y=cut, color=color)) +
  xlab("CARAT OF DIAMOND") +
  ylab("CUT OF DIAMOND")

```


####Data munging and wrangling

1.) 

```{r}
spread(table2, key=type,value=count)

```

2.) 

```{r}
diamonds %>% 
  mutate(price_per_carat = price/carat)

```

3.)
```{r}

```


####EDA
